A Data-Driven Framework for Neural Field Modelling

### 2010-11-08 ltx/first_order_framework/LaTeX_Manuscript.tex
added xi mean and std to the result table

\small{\begin{tabular}{lccccccccc}
Experiment&\multicolumn{3}{c}{I}&\multicolumn{3}{c}{II}&\multicolumn{3}{c}{III}\\
 Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
\hline\hline
Actual Value&$90$&$-80$&$5$&$100$&$-80$&$5$&$110$&$-80$&$5$\\
Mean Estimate&$103.86$&$-89.05$&$5.23$&$101.75$&$-81.00$&$4.76$&$98.90 $&$-73.13$&$4.37$\\
Std. Dev.&$23.14$&$16.57$&$0.74$&$21.30$&$14.82$&$0.65$&$16.48$& $11.72$&$0.54$\\
Bias (\%)& $15.4$&$11.31$&$4.6$&$1.75$&$1.25$&$4.8$&$10.1$&$ 8.58$&$12.6$  \\
\end{tabular}}

\small{\begin{tabular}{lccccccccc}
Experiment&\multicolumn{3}{c}{IV}&\multicolumn{3}{c}{V}&\multicolumn{3}{c}{VI}\\
 Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
\hline\hline
Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
Mean Estimate&$35.68$&$-18.16$&$0.81$&$40.43$&$-12.01$&$ 0.35$&$61.46$&$-15.03$&$0.27$\\
Std. Dev.&$16.72$&$11.77$&$0.53$&$11.47$&$7.8$&$0.36$&$11.51$&$7.56$&$0.29$\\
Bias (\%)&$137.87$&$-$&$-$&$34.77$&$-$&$-$&$22.92$&$-$&$-$\\
\end{tabular}}

>>>>

\tiny{\begin{tabular}{lcccccccccccc}
Experiment&\multicolumn{4}{c}{I}&\multicolumn{4}{c}{II}&\multicolumn{4}{c}{III}\\
 Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
\hline\hline
Actual Value&$90$&$-80$&$5$&$0.9$&$100$&$-80$&$5$&$0.9$&$110$&$-80$&$5$&$0.9$\\
Mean Estimate&$103.86$&$-89.05$&$5.23$&$0.923$&$101.75$&$-81.00$&$4.76$&$0.924$&$98.90 $&$-73.13$&$4.37$&$0.925$\\
Std. Dev.&$23.14$&$16.57$&$0.74$&$0.003$&$21.30$&$14.82$&$0.65$&$0.003$&$16.48$& $11.72$&$0.54$&$0.003$\\
Bias (\%)& $15.4$&$11.31$&$4.6$&$2.56$&$1.75$&$1.25$&$4.8$&$2.67$&$10.1$&$ 8.58$&$12.6$&$2.78$  \\
\end{tabular}}

\tiny{\begin{tabular}{lcccccccccccc}
Experiment&\multicolumn{4}{c}{IV}&\multicolumn{4}{c}{V}&\multicolumn{4}{c}{VI}\\
 Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$&$\theta_0$&$\theta_1$&$\theta_2$&$\xi$\\
\hline\hline
Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
Mean Estimate&$35.68$&$-18.16$&$0.81$&$0.923$&$40.43$&$-12.01$&$ 0.35$&$0.924$&$61.46$&$-15.03$&$0.27$&$0.924$\\
Std. Dev.&$16.72$&$11.77$&$0.53$&$0.002$&$11.47$&$7.8$&$0.36$&$0.003$&$11.51$&$7.56$&$0.29$&$0.003$\\
Bias (\%)&$137.87$&$-$&$-$&$2.56$&$34.77$&$-$&$-$&$2.67$&$22.92$&$-$&$-$&$2.67$\\
\end{tabular}}
